---
title: "Descriptive Statistics"
author: "Erin Buchanan"
date: "`r Sys.Date()`"
output: html_document
bibliography: references.bib
---

```{r setup, include=FALSE, echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, size="scriptsize")
def.chunk.hook <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})
```

```{r libraries, include=FALSE, echo = FALSE, message = FALSE, warning = FALSE}
library(rio)
library(dplyr)
library(ggplot2)
library(tidyverse)
library(uaparserjs)
library(papaja)
library(flextable)
library(psych)
```

```{r import-merge}
native.trans <- import("recoding_files/native_trans.xlsx")
browser.lang <- import("recoding_files/browser_language.xlsx") %>% 
  mutate(Language = gsub(" \\(.*\\)", "", Language),
         Language = trimws(Language))
  
```

```{r import-participant}
# open all participant data
p.list <- list.files(
  path = "../05_Data/data_processing/output_data",
  full.names = TRUE,
  recursive = TRUE,
  pattern = "*.participant_data.csv"
)

# import files
p.files <- lapply(p.list, import)

# give them names 
names(p.files) <- gsub("../05_Data/data_processing/output_data/participant_data/|_participant_data.csv", "", p.list)

# deal with mismatches
for (i in 1:length(p.files)){
  p.files[[i]]$url_lab <- as.character(p.files[[i]]$url_lab)
}

# merge them together
p.df <- bind_rows(p.files)
p.df$language <- rep(names(p.files), times = unlist(lapply(p.files, nrow)))

# native translation
p.df <- p.df %>% 
  mutate(native_language = tolower(native_language)) %>% 
  left_join(
    native.trans %>% 
      select(listed, `Official Translation`) %>% 
      dplyr::rename(native_language_translated = `Official Translation`) %>% 
      mutate(listed = tolower(listed)) %>% 
      unique(),
    by = c("native_language" = "listed")
  ) %>% 
  mutate(native_language_translated = 
           ifelse(is.na(native_language)|native_language == "", "Missing", 
                  native_language_translated)) 

# recode missing
p.df <- p.df %>% 
   mutate(please_tell_us_your_gender = 
           ifelse(is.na(please_tell_us_your_gender)|please_tell_us_your_gender == "", "Missing", 
                  please_tell_us_your_gender), 
          please_tell_us_your_education_level = 
           ifelse(is.na(please_tell_us_your_education_level)|please_tell_us_your_education_level == "", "Missing", 
                  please_tell_us_your_education_level),
          meta_platform = ifelse(is.na(meta_platform)|meta_platform == "",
          "Missing", meta_platform))

# age
p.df <- p.df %>% 
  mutate(year_exp = as.numeric(substr(timestamp_consent,1,4)), 
         age = year_exp - which_year_were_you_born)

# browser
browsers <- ua_parse(p.df$meta_user_agent) %>% 
  unique() %>% 
  select(userAgent, ua.family)

p.df <- p.df %>% 
  left_join(
    browsers, 
    by = c("meta_user_agent" = "userAgent")
  ) %>% 
  mutate(meta_locale = tolower(meta_locale)) %>% 
  left_join(
    browser.lang %>% 
      dplyr::rename("browser_language" = "Language") %>% 
      unique(),
    by = c("meta_locale" = "Code")
  ) 

# ones to fix
temp <- 
  as.data.frame(table(p.df$meta_locale, 
                      p.df$browser_language, useNA = "ifany")) %>% 
  filter(Freq > 0) %>% 
  filter(is.na(Var2))

# export(temp, "browser_codes.csv", row.names = F)

p.df <- p.df %>% 
  mutate(please_tell_us_your_gender = factor(please_tell_us_your_gender, 
                                             levels = c("Missing", "female", 
                                                        "male", "notsay", "other"), 
                                             labels = c("Missing", "Female", 
                                                        "Male", "Not Say", "Other")),
         please_tell_us_your_education_level = factor(please_tell_us_your_education_level, 
                                                      levels = c("Missing", 
                                                                 "less than high school", 
                                                                 "high school",
                                                                 "some college",
                                                                 "college", 
                                                                 "master",
                                                                 "doctorate"),
                                                      labels = c("Missing", 
                                                                 "Less than High School",
                                                                 "High School", 
                                                                 "Some College",
                                                                 "College", 
                                                                 "Masters", 
                                                                 "Doctorate")))
```

```{r update-native, eval = F}
native.df <- p.df %>% 
  select(native_language, meta_language, language) %>% 
  unique() %>% 
  filter(!(duplicated(native_language))) %>% 
  full_join(
    native.trans, 
    by = c("native_language" = "listed",
           "meta_language" = "meta_language",
           "language" = "lang")
  )

# used to create native_trans files 
export(native.df, "recoding_files/native_answers.xlsx", row.names = F)

# View(table(p.df$native_language_translated, useNA = "ifany"))
```

Please note that this file only includes languages that are analyzed in the full paper. You can view complete data demographics by using this markdown file and turning off the data filter.

```{r filter-data, eval = T}
# change eval = T to eval = F to get the full dataset 
langs <- c("cs", "da", "de", 
           "el", "en", "es", "fr", "hu", "it", "ja", 
           "ko", "pl", "pt_combo", 
           "ro", "ru", "sr", "tr", 
           "zh")

p.df <- p.df %>% 
  filter(language %in% langs)
```

The links to the language files can be found in our supplemental materials. The paper is presented with an upcoming *R* package `semanticprimeR` that allows one to open data files directly in *R* and a Shiny application to download a specific set of language files [@shiny; @thedoomlab2024]. The data can be cited using our Zenodo doi [@buchanan2024] which will indicate which version of the data was examined.

# Participant level data

## Gender

```{r gender-split}
p.overall.gender <- p.df %>% 
  group_by(please_tell_us_your_gender) %>% 
  summarize(freq.gender = n() / nrow(.) * 100,
            .groups = "keep") 

p.keep.gender <- p.df %>% 
  filter(keep == "keep") %>% 
  group_by(please_tell_us_your_gender) %>% 
  summarize(freq.gender = n() / nrow(.) * 100,
            .groups = "keep") 

p.keepanswered.gender <- p.df %>% 
  filter(keep_answered == "keep") %>% 
  group_by(please_tell_us_your_gender) %>% 
  summarize(freq.gender = n() / nrow(.) * 100,
            .groups = "keep") 
```

Participants were generally female (`r apa_num(p.overall.gender %>% filter(please_tell_us_your_gender == "Female") %>% pull(freq.gender))`%) or male (`r apa_num(p.overall.gender %>% filter(please_tell_us_your_gender == "Male") %>% pull(freq.gender))`)% with the rest either missing data, not wanting to indicate their gender or other. If data was filtered to only participants that were kept for analysis, the data was again predominantly female (`r apa_num(p.keep.gender %>% filter(please_tell_us_your_gender == "Female") %>% pull(freq.gender))`%) or male (`r apa_num(p.keep.gender %>% filter(please_tell_us_your_gender == "Male") %>% pull(freq.gender))`)%.

### Overall Gender

```{r overall-gender}
flextable(p.overall.gender) %>% 
  set_header_labels(x = ., 
                    values = c("Gender", "Percent")) %>% 
  colformat_double(
  x = .,
  big.mark = ",", digits = 2, na_str = "N/A"
)
```

### Gender for Original Accuracy Participants

```{r keep-gender}
flextable(p.keep.gender) %>% 
  set_header_labels(x = ., 
                    values = c("Gender", "Percent")) %>% 
  colformat_double(
  x = .,
  big.mark = ",", digits = 2, na_str = "N/A"
)
```

### Gender for Rescored Accuracy Participants

```{r answered-gender}
flextable(p.keepanswered.gender) %>% 
  set_header_labels(x = ., 
                    values = c("Gender", "Percent")) %>% 
  colformat_double(
  x = .,
  big.mark = ",", digits = 2, na_str = "N/A"
)
```

## Education Levels

```{r education-split}
p.overall.education <- p.df %>% 
  group_by(please_tell_us_your_education_level) %>% 
  summarize(freq.education = n() / nrow(.) * 100,
            .groups = "keep") 

p.keep.education <- p.df %>% 
  filter(keep == "keep") %>% 
  group_by(please_tell_us_your_education_level) %>% 
  summarize(freq.education = n() / nrow(.) * 100,
            .groups = "keep") 

p.keepanswered.education <- p.df %>% 
  filter(keep_answered == "keep") %>% 
  group_by(please_tell_us_your_education_level) %>% 
  summarize(freq.education = n() / nrow(.) * 100,
            .groups = "keep") 
```

Participants indicated they had completed high school (`r apa_num(p.overall.education %>% filter(please_tell_us_your_education_level == "High School") %>% pull(freq.education))`%), some college (`r apa_num(p.overall.education %>% filter(please_tell_us_your_education_level == "Some College") %>% pull(freq.education))`%), college (`r apa_num(p.overall.education %>% filter(please_tell_us_your_education_level == "College") %>% pull(freq.education))`%), master's (`r apa_num(p.overall.education %>% filter(please_tell_us_your_education_level == "Masters") %>% pull(freq.education))`%), and the rest other options (Less than High School, Missing, or Doctorate). Participants kept for analysis also followed this pattern: high school (`r apa_num(p.keep.education %>% filter(please_tell_us_your_education_level == "High School") %>% pull(freq.education))`%), some college (`r apa_num(p.keep.education %>% filter(please_tell_us_your_education_level == "Some College") %>% pull(freq.education))`%), college (`r apa_num(p.keep.education %>% filter(please_tell_us_your_education_level == "College") %>% pull(freq.education))`%), master's (`r apa_num(p.keep.education %>% filter(please_tell_us_your_education_level == "Masters") %>% pull(freq.education))`%).

### Overall Education

```{r overall-education}
flextable(p.overall.education) %>% 
  set_header_labels(x = ., 
                    values = c("Education", "Percent")) %>% 
  colformat_double(
  x = .,
  big.mark = ",", digits = 2, na_str = "N/A"
)
```

### Education for Original Accuracy Participants

```{r keep-education}
flextable(p.keep.education) %>% 
  set_header_labels(x = ., 
                    values = c("Education", "Percent")) %>% 
  colformat_double(
  x = .,
  big.mark = ",", digits = 2, na_str = "N/A"
)
```

### Education for Rescored Accuracy Participants

```{r answered-education}
flextable(p.keepanswered.education) %>% 
  set_header_labels(x = ., 
                    values = c("Education", "Percent")) %>% 
  colformat_double(
  x = .,
  big.mark = ",", digits = 2, na_str = "N/A"
)
```

## Native Language

```{r n_lang-split}
p.overall.n_lang <- p.df %>% 
  group_by(native_language_translated) %>% 
  summarize(freq.n_lang = n() / nrow(.) * 100,
            .groups = "keep") %>% 
  ungroup() %>% 
  dplyr::arrange(desc(freq.n_lang)) 

p.keep.n_lang <- p.df %>% 
  filter(keep == "keep") %>% 
  group_by(native_language_translated) %>% 
  summarize(freq.n_lang = n() / nrow(.) * 100,
            .groups = "keep") %>% 
  ungroup() %>% 
  dplyr::arrange(desc(freq.n_lang)) 

p.keepanswered.n_lang <- p.df %>% 
  filter(keep_answered == "keep") %>% 
  group_by(native_language_translated) %>% 
  summarize(freq.n_lang = n() / nrow(.) * 100,
            .groups = "keep") %>% 
  ungroup() %>% 
  dplyr::arrange(desc(freq.n_lang)) 

p.toptwenty.n_lang <- p.overall.n_lang %>% 
  slice(1:20) %>% 
  full_join(p.keep.n_lang %>% 
  slice(1:20), 
  by = c("native_language_translated")) %>% 
  dplyr::rename(
    "Overall Percent" = freq.n_lang.x,
    "Keep Percent" = freq.n_lang.y
  )
```

The top twenty native languages represented in the data are shown in Table X. Full language percent tables can be found in the supplemental data. The data indicates that the pattern of native languages are similar in the full data and data used for analysis.

```{r overall-n_lang-table}
flextable(p.toptwenty.n_lang) %>% 
  set_header_labels(x = ., 
                    values = c("Native Language", "Overall Percent", 
                               "Keep Percent")) %>% 
  colformat_double(
  x = .,
  big.mark = ",", digits = 2, na_str = "N/A"
)
```

### Overall Native Language

Please see https://osf.io/ta6wf for a summarized list of all native languages.

```{r overall-n_lang}
export(p.overall.n_lang, "supplemental/overall_native_language.csv", row.names = F)
```

### Native Language for Original Accuracy Participants

Please see https://osf.io/652h8 for a summarized list of all native languages for participants used in analysis.

```{r keep-n_lang}
export(p.keep.n_lang, "supplemental/keep_native_language.csv", row.names = F)
```

### Native Language for Rescored Accuracy Participants

Please see https://osf.io/b3y6r for a summarized list of all native languages for rescored accuracy in native language.

```{r answered-n_lang}
export(p.keepanswered.n_lang, "supplemental/keep_answered_native_language.csv", row.names = F)
```

## Average Age

```{r age-split}
p.overall.age <- describe(p.df$age, na.rm = T)

p.keep.age <- describe(p.df$age[p.df$keep == "keep"], na.rm = T)

p.keepanswered.age <- describe(p.df$age[p.df$keep_answered == "keep"], na.rm = T)
```

The average age for all participants was $M$ = `r apa_num(p.overall.age$mean)` ($SD$ = `r apa_num(p.overall.age$sd)`) ranging from `r apa_num(p.overall.age$min)` to `r apa_num(p.overall.age$max)`. The demographic question asked participants to enter their year of birth, and the high maximum values were likely participants who entered the minimum possible year allowable in the data collection form. The participants kept for analysis showed the same pattern of ages: $M$ = `r apa_num(p.keep.age$mean)` ($SD$ = `r apa_num(p.keep.age$sd)`) ranging from `r apa_num(p.keep.age$min)` to `r apa_num(p.keep.age$max)`.

The rescored accuracy participants showed the following age pattern: $M$ = `r apa_num(p.keepanswered.age$mean)` ($SD$ = `r apa_num(p.keepanswered.age$sd)`) ranging from `r apa_num(p.keepanswered.age$min)` to `r apa_num(p.keepanswered.age$max)`.

## Operating System

```{r overall-os}
p.df <- p.df %>% 
  mutate(meta_platform_recode = ifelse(
    grepl("Win", meta_platform), "Windows", ifelse(
      grepl("Linux", meta_platform), "Linux", ifelse(
        grepl("Mac", meta_platform), "Mac", meta_platform
      )
    )
  )
)

p.overall.os <- p.df %>% 
  group_by(meta_platform_recode) %>% 
  summarize(freq.os = n() / nrow(.) * 100,
            .groups = "keep") 

p.keep.os <- p.df %>% 
  filter(keep == "keep") %>% 
  group_by(meta_platform_recode) %>% 
  summarize(freq.os = n() / nrow(.) * 100,
            .groups = "keep") 

p.keepanswered.os <- p.df %>% 
  filter(keep_answered == "keep") %>% 
  group_by(meta_platform_recode) %>% 
  summarize(freq.os = n() / nrow(.) * 100,
            .groups = "keep") 
```

The majority of participants used a Windows based operating system (`r apa_num(p.overall.os %>% filter(meta_platform_recode == "Windows") %>% pull(freq.os))`%) followed by Mac OS (`r apa_num(p.overall.os %>% filter(meta_platform_recode == "Mac") %>% pull(freq.os))`%), and Linux (`r apa_num(p.overall.os %>% filter(meta_platform_recode == "Linux") %>% pull(freq.os))`%), with some missing data (`r apa_num(p.overall.os %>% filter(meta_platform_recode == "Missing") %>% pull(freq.os))`%). The operating systems were the same for the participants used in analysis: Windows (`r apa_num(p.keep.os %>% filter(meta_platform_recode == "Windows") %>% pull(freq.os))`%), Mac (`r apa_num(p.keep.os %>% filter(meta_platform_recode == "Mac") %>% pull(freq.os))`%), Linux (`r apa_num(p.keep.os %>% filter(meta_platform_recode == "Linux") %>% pull(freq.os))`%), and Missing (`r apa_num(p.keep.os %>% filter(meta_platform_recode == "Missing") %>% pull(freq.os))`%).

### Overall Operating System

```{r overall-os}
flextable(p.overall.os) %>% 
  set_header_labels(x = ., 
                    values = c("Operating System", "Percent")) %>% 
  colformat_double(
  x = .,
  big.mark = ",", digits = 2, na_str = "N/A"
)
```

### Operating System for Original Accuracy Participants

```{r keep-os}
flextable(p.keep.os) %>% 
  set_header_labels(x = ., 
                    values = c("Operating System", "Percent")) %>% 
  colformat_double(
  x = .,
  big.mark = ",", digits = 2, na_str = "N/A"
)
```

### Operating System for Rescored Accuracy Participants

```{r answered-os}
flextable(p.keepanswered.os) %>% 
  set_header_labels(x = ., 
                    values = c("Operating System", "Percent")) %>% 
  colformat_double(
  x = .,
  big.mark = ",", digits = 2, na_str = "N/A"
)
```

## Web Browser

```{r overall-web}
p.df <- p.df %>% 
  mutate(ua.family_recode = ifelse(
    grepl("Chrome", ua.family), "Chrome", ifelse(
      grepl("Edge", ua.family), "Edge", ifelse(
        grepl("Firefox", ua.family), "Firefox", ifelse(
          grepl("Opera", ua.family), "Opera", ifelse(
            grepl("Safari", ua.family), "Safari", ifelse(
              grepl("Yandex", ua.family), "Yandex", "Other"
            )
          )
        )
      )
    )
  )
)

p.overall.web <- p.df %>% 
  group_by(ua.family_recode) %>% 
  summarize(freq.web = n() / nrow(.) * 100,
            .groups = "keep") 

p.keep.web <- p.df %>% 
  filter(keep == "keep") %>% 
  group_by(ua.family_recode) %>% 
  summarize(freq.web = n() / nrow(.) * 100,
            .groups = "keep") 

p.keepanswered.web <- p.df %>% 
  filter(keep_answered == "keep") %>% 
  group_by(ua.family_recode) %>% 
  summarize(freq.web = n() / nrow(.) * 100,
            .groups = "keep") 
```

Web browsers were grouped into the largest categories for reporting. The large majority of participants used Chrome (`r apa_num(p.overall.web %>% filter(ua.family_recode == "Chrome") %>% pull(freq.web))`%), followed by Edge (`r apa_num(p.overall.web %>% filter(ua.family_recode == "Edge") %>% pull(freq.web))`%), Firefox (`r apa_num(p.overall.web %>% filter(ua.family_recode == "Firefox") %>% pull(freq.web))`%), Safari (`r apa_num(p.overall.web %>% filter(ua.family_recode == "Safari") %>% pull(freq.web))`%), and Opera (`r apa_num(p.overall.web %>% filter(ua.family_recode == "Opera") %>% pull(freq.web))`%) A surprise result was that the Russian browser Yandex contributed a small (but not extremely small) percent of the browser usage: (`r apa_num(p.overall.web %>% filter(ua.family_recode == "Yandex") %>% pull(freq.web))`%), followed by other web browsers (`r apa_num(p.overall.web %>% filter(ua.family_recode == "Other") %>% pull(freq.web))`%) The results were the same when examining participants who were kept for analysis: Chrome (`r apa_num(p.keep.web %>% filter(ua.family_recode == "Chrome") %>% pull(freq.web))`%), Edge (`r apa_num(p.keep.web %>% filter(ua.family_recode == "Edge") %>% pull(freq.web))`%), Firefox (`r apa_num(p.keep.web %>% filter(ua.family_recode == "Firefox") %>% pull(freq.web))`%), Safari (`r apa_num(p.keep.web %>% filter(ua.family_recode == "Safari") %>% pull(freq.web))`%), Opera (`r apa_num(p.keep.web %>% filter(ua.family_recode == "Opera") %>% pull(freq.web))`%), Yandex (`r apa_num(p.keep.web %>% filter(ua.family_recode == "Yandex") %>% pull(freq.web))`%), and Other (`r apa_num(p.keep.web %>% filter(ua.family_recode == "Other") %>% pull(freq.web))`%). 

### Overall Web Browser

```{r overall-web}
flextable(p.overall.web) %>% 
  set_header_labels(x = ., 
                    values = c("Web Browser", "Percent")) %>% 
  colformat_double(
  x = .,
  big.mark = ",", digits = 2, na_str = "N/A"
)
```

### Web Browser for Original Accuracy Participants

```{r keep-web}
flextable(p.keep.web) %>% 
  set_header_labels(x = ., 
                    values = c("Web Browser", "Percent")) %>% 
  colformat_double(
  x = .,
  big.mark = ",", digits = 2, na_str = "N/A"
)
```

### Web Browser for Rescored Accuracy Participants

```{r answered-web}
flextable(p.keepanswered.web) %>% 
  set_header_labels(x = ., 
                    values = c("Web Browser", "Percent")) %>% 
  colformat_double(
  x = .,
  big.mark = ",", digits = 2, na_str = "N/A"
)
```

## Language Locale

```{r overall-locale}
p.df <- p.df %>% 
  mutate(browser_language = ifelse(
      is.na(browser_language), "Missing", browser_language
    )
  )

p.overall.locale <- p.df %>% 
  group_by(browser_language) %>% 
  summarize(freq.locale = n() / nrow(.) * 100,
            .groups = "keep") %>% 
  ungroup() %>% 
  dplyr::arrange(desc(freq.locale))

p.keep.locale <- p.df %>% 
  filter(keep == "keep") %>% 
  group_by(browser_language) %>% 
  summarize(freq.locale = n() / nrow(.) * 100,
            .groups = "keep") %>% 
  ungroup() %>% 
  dplyr::arrange(desc(freq.locale))

p.keepanswered.locale <- p.df %>% 
  filter(keep_answered == "keep") %>% 
  group_by(browser_language) %>% 
  summarize(freq.locale = n() / nrow(.) * 100,
            .groups = "keep") %>% 
  ungroup() %>% 
  dplyr::arrange(desc(freq.locale))

p.toptwenty.locale <- p.overall.locale %>% 
  slice(1:20) %>% 
  full_join(p.keep.locale %>% 
  slice(1:20), 
  by = c("browser_language")) %>% 
  dplyr::rename(
    "Overall Percent" = freq.locale.x,
    "Keep Percent" = freq.locale.y
  )
```

The top twenty browser languages represented in the data are shown in Table X, with full tables of browser languages in the supplemental online data. Generally, this pattern matched the demographics of the study, as well as the targeted languages. More participants had their browser set in English compared to the indicated native language, see Table X. 

```{r overall-locale-table}
flextable(p.toptwenty.locale) %>% 
  set_header_labels(x = ., 
                    values = c("Browser Language", "Overall Percent", 
                               "Keep Percent")) %>% 
  colformat_double(
  x = .,
  big.mark = ",", digits = 2, na_str = "N/A"
)
```

### Overall Browser Language

Please see https://osf.io/93kep for a summarized list of all browser languages.

```{r overall-locale}
export(p.overall.locale, "supplemental/overall_browser_language.csv", row.names = F)
```

### Browser Language for Original Accuracy Participants

Please see https://osf.io/3yab7 for a summarized list of all browser languages for participants used in analysis.

```{r keep-locale}
export(p.keep.locale, "supplemental/keep_browser_language.csv", row.names = F)
```

### Native Language for Rescored Accuracy Participants

Please see https://osf.io/adhbe for a summarized list of all browser languages for rescored accuracy in native language.

```{r answered-locale}
export(p.keepanswered.locale, "supplemental/keep_answered_browser_language.csv", row.names = F)
```

## Data by Lab

Please see summary report located at: https://osf.io/ty4hp which includes gender, education, age, and sample size counts for a summary. This table also includes information about the ethics submissions and data collection procedures for each lab.

- Native Language by Lab: https://osf.io/hnrgk
- Operating System by Lab: https://osf.io/gud6v
- Web Browser by Lab: https://osf.io/egk9w
- Language Locale by Lab: https://osf.io/wt3xn

```{r separate-by-lab}
p.df %>% 
  group_by(url_lab, native_language_translated) %>% 
  summarize(frequency = n(), .groups = "keep") %>% 
  mutate(url_lab = paste0("lab_", url_lab)) %>% 
  pivot_wider(data = ., 
              names_from = url_lab, 
              values_from = frequency,
              values_fill = 0) %>% 
  export(., "supplemental/lab_native_language.csv", row.names = F)

p.df %>% 
  group_by(url_lab, meta_platform) %>% 
  summarize(frequency = n(), .groups = "keep") %>% 
  mutate(url_lab = paste0("lab_", url_lab)) %>% 
  pivot_wider(data = ., 
              names_from = url_lab, 
              values_from = frequency,
              values_fill = 0) %>% 
  export(., "supplemental/lab_operating_system.csv", row.names = F)

p.df %>% 
  group_by(url_lab, ua.family) %>% 
  summarize(frequency = n(), .groups = "keep") %>% 
  mutate(url_lab = paste0("lab_", url_lab)) %>% 
  pivot_wider(data = ., 
              names_from = url_lab, 
              values_from = frequency,
              values_fill = 0) %>% 
  export(., "supplemental/lab_web_browser.csv", row.names = F)

p.df %>% 
  group_by(url_lab, browser_language) %>% 
  summarize(frequency = n(), .groups = "keep") %>% 
  mutate(url_lab = paste0("lab_", url_lab)) %>% 
  pivot_wider(data = ., 
              names_from = url_lab, 
              values_from = frequency,
              values_fill = 0) %>% 
  export(., "supplemental/lab_lang_locale.csv", row.names = F)
  
```

## Data by Language

Please see summary report located at: https://osf.io/y3dk7. This summary includes gender, education, and age information by language.

- Native Language by Language:
- Operating System by Language:
- Web Browser by Language:
- Language Locale by Language:

```{r separate-by-lang}
p.df %>% 
  group_by(language, native_language_translated) %>% 
  summarize(frequency = n(), .groups = "keep") %>% 
  pivot_wider(data = ., 
              names_from = language, 
              values_from = frequency,
              values_fill = 0) %>% 
  export(., "supplemental/lang_native_language.csv", row.names = F)

p.df %>% 
  group_by(language, meta_platform) %>% 
  summarize(frequency = n(), .groups = "keep") %>% 
  pivot_wider(data = ., 
              names_from = language, 
              values_from = frequency,
              values_fill = 0) %>% 
  export(., "supplemental/lang_operating_system.csv", row.names = F)

p.df %>% 
  group_by(language, ua.family) %>% 
  summarize(frequency = n(), .groups = "keep") %>% 
  pivot_wider(data = ., 
              names_from = language, 
              values_from = frequency,
              values_fill = 0) %>% 
  export(., "supplemental/lang_web_browser.csv", row.names = F)

p.df %>% 
  group_by(language, browser_language) %>% 
  summarize(frequency = n(), .groups = "keep") %>% 
  pivot_wider(data = ., 
              names_from = language, 
              values_from = frequency,
              values_fill = 0) %>% 
  export(., "supplemental/lang_lang_locale.csv", row.names = F)
```

We will present descriptive statistics on the participants involved in the study including percentages of gender, education levels, native language, and average age. Information about the device used to complete the study will include percentages of computer operating system, the web browser, and the language locale (i.e., the language the browser defaults to using).

make a map picture by where labs were recruiting - figure out how to deal with prolific, mturk, qualtrics, bilendi

# Trial level data

Each language is saved in separate files, and supplemental files and code are provided to merge trials across concepts and pairings (i.e., CAT [English] → KATZE [German] → GATTA [Italian]). If a participant left the study early (e.g., Internet disconnection, computer crash, closes the study), the data past this point in the study is not recorded, and therefore, the trial level data represents all trials displayed during the experiment. Participants were expected to incorrectly answer trials, and these trials were marked for exclusion. All timeout trials were marked as missing values in the final data. No missing values were imputed.

Trials were marked for exclusion if they were under the minimum response latency of less than 160 ms (i.e., all trials will be presented in the trial level data for openness, but these will be excluded for analysis and calculations listed below). Further, labjs automatically codes timeout data with a special marker (i.e., data ended on response or timeout as a column), which excludes trials over 3000 ms as our maximum response latency. However, due to differences in browser/screen refresh rates, some trials were answered with response latencies over 3000 ms when a participant made a key press at the very end of the trial before timeout. Given our pre-registered exclusion rules, these were also marked for exclusion.

The response latencies from each participant’s session were then *z*-scored in line with recommendations from Faust et al.[@faust1999]. We did not collect enough data to note if a person took the experiment multiple times for privacy reasons, but as these are considered different sessions, the recommended *z*-score procedure should control for participant variability at this level. Therefore, repeated participation was not be detrimental to data collection. Finally, participants' overall proportion of correct answers was calculated, and participants who did not correctly answer at least 80% of 100 minimum trials were marked for exclusion for item data, priming data, and analysis. The average error in the Semantic Priming Project ranged from 4% to 5%, and this criterion was chosen to include participants who were focused on the task. Please see summary of exclusion criteria for all exclusions, which are marked separately in the provided data files. Additionally, as noted above, accuracy was defined multiple ways by the lead team, and therefore, both criteria are provided.

We will provide descriptive statistics on the average time to complete the study, the number of trials by word type (word, nonword), the accuracy by word type, and average z-scored response latencies by word type (overall, excluding Z \> 2.5, excluding Z \> 3.0; see below). These values will be provided for overall results and separated by language.

```{r}

```

# Item level data

The item data files contain lexical information about all stimuli calculated from the OpenSubtitles23 and subs2vec55 projects (length, frequency, orthographic neighborhood, bigram frequency, orthographic and phonographic Levenshtein distance). The descriptive statistics calculated from the trial level data will then be included: mean response latency, average standardized response latency, sample size, standard errors of response latencies, and accuracy rate. No data will be excluded for being a potential outlier; however, we will recommend a cut-off criterion for absolute value z-score outliers at 2.5 and 3.0, and we will calculate these same statistics with those subsets of trials excluded. For all real words, the age of acquisition, imageability, concreteness, valence, dominance, arousal, and familiarity values will be included. These values do not exist for non-words. 24

We will provide descriptive statistics on the average sample size, average z-scored response latencies, and average SE for the z-scored response latencies by each word type (word, nonword). These values will be calculated for the overall data set, separated by language, and without each level of z-score outlier criterion.

# Priming data

add note about overall proportions of priming trials calculate transition probabilities

In a separate file, we will also prepare information about priming results which includes the target word, average response latencies, averaged Z-scored response latencies, sample sizes, standard errors, and priming response latency. For each item, priming is defined as the average z-scored response latency when presented in the unrelated minus the related condition. Therefore, the timing for DOG-CAT would be subtracted from BUS-CAT to indicate priming for the word CAT. The similarity scores calculated during stimuli selection will be provided in this file, as well as other popular measures of similarity if they are available in that language. For example, semantic feature overlap norms are also available in Italian95, German96, Spanish26, and Dutch97.

We will provide the average statistics for z-score priming, z-score unrelated response latency, z-score related response latency, sample size for unrelated trials, and sample size for related trials. These values will be calculated overall, by language, and with/without z- score level exclusions. Last, we will calculate the participant level priming reliability98 and item-level priming reliability44.
