---
title: "Descriptive Statistics"
author: "Erin Buchanan"
date: "`r Sys.Date()`"
output: html_document
bibliography: references.bib
---

```{r setup, include=FALSE, echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, size="scriptsize")
def.chunk.hook <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})
```

```{r libraries, include=FALSE, echo = FALSE, message = FALSE, warning = FALSE}
library(rio)
library(dplyr)
library(ggplot2)
library(maps)
library(tidyverse)
library(uaparserjs)
library(papaja)
library(flextable)
library(psych)
library(countrycode)
```

The links to the language files can be found in our supplemental materials. The paper is presented with an upcoming *R* package `semanticprimeR` that allows one to open data files directly in *R* and a Shiny application to download a specific set of language files [@shiny; @thedoomlab2024]. The data can be cited using our Zenodo doi [@buchanan2024] which will indicate which version of the data was examined.

# Priming data

In a separate file, we prepared information about priming results which includes the target word, average response latencies, averaged *Z*-scored response latencies, sample sizes, standard errors, and priming response latency. For each item, priming is defined as the average *Z*-scored response latency when presented in the unrelated minus the related condition. Therefore, the timing for DOG-CAT would be subtracted from BUS-CAT to indicate priming for the word CAT. The similarity scores calculated during stimuli selection will be provided for merging, as well as other popular measures of similarity if they are available in that language. For example, semantic feature overlap norms are also available in Italian [@montefinese2013], German [@kremer2011], Spanish [@aguasvivas2018], and Dutch [@ruts2004].

## Original Accuracy Priming Scores

```{r keep-get-priming}
langs <- c("cs", "da", "de", 
           "el", "en", "es", "fr", "hu", "it", "ja", 
           "ko", "pl", "pt_combo", "br_pt_combo",
           "ro", "ru", "sr", "tr", 
           "zh")

# open all participant data
prime.list <- list.files(
  path = "../05_Data/data_processing/output_data",
  full.names = TRUE,
  recursive = TRUE,
  pattern = "*prime_summary.csv"
)

# only languages we need
langs_trial <- paste(paste0("/", langs, "_prime"), collapse = "|")
prime.list <- prime.list[grepl(langs_trial, prime.list)]

# import files
prime.files <- lapply(prime.list, import)

# give them names 
names(prime.files) <- gsub("../05_Data/data_processing/output_data/priming_data/|_prime_summary.csv|_combo", "", prime.list)

# merge them together
prime.df <- bind_rows(prime.files)
prime.df$language <- rep(names(prime.files), times = unlist(lapply(prime.files, nrow)))
prime.df$z_type <- "All"
```

```{r keep-get-priming2}
# open all participant data
prime.list <- list.files(
  path = "../05_Data/data_processing/output_data",
  full.names = TRUE,
  recursive = TRUE,
  pattern = "*prime_summary_no2.5.csv"
)

# only languages we need
langs_trial <- paste(paste0("/", langs, "_prime"), collapse = "|")
prime.list <- prime.list[grepl(langs_trial, prime.list)]

# import files
prime.files <- lapply(prime.list, import)

# give them names 
names(prime.files) <- gsub("../05_Data/data_processing/output_data/priming_data/|_prime_summary_no2.5.csv|_combo", "", prime.list)

# merge them together
prime.df2 <- bind_rows(prime.files)
prime.df2$language <- rep(names(prime.files), times = unlist(lapply(prime.files, nrow)))
prime.df2$z_type <- "2.5"
```

```{r keep-get-priming3}
# open all participant data
prime.list <- list.files(
  path = "../05_Data/data_processing/output_data",
  full.names = TRUE,
  recursive = TRUE,
  pattern = "*prime_summary_no3.0.csv"
)

# only languages we need
langs_trial <- paste(paste0("/", langs, "_prime"), collapse = "|")
prime.list <- prime.list[grepl(langs_trial, prime.list)]

# import files
prime.files <- lapply(prime.list, import)

# give them names 
names(prime.files) <- gsub("../05_Data/data_processing/output_data/priming_data/|_prime_summary_no3.0.csv|_combo", "", prime.list)

# merge them together
prime.df3 <- bind_rows(prime.files)
prime.df3$language <- rep(names(prime.files), times = unlist(lapply(prime.files, nrow)))
prime.df3$z_type <- "3.0"
```

```{r keep-calc-priming}
# z priming, z unrelated, z related, sample unrelated, sample related
prime.df.all <- bind_rows(
  prime.df,
  prime.df2,
  prime.df3
)

prime.overall <- prime.df.all %>% 
  group_by(z_type) %>% 
  summarize(m_prime = mean(avgZ_prime, na.rm = T),
            m_unrel = mean(avgZ_RT_unrelated, na.rm = T),
            m_rel = mean(avgZ_RT_related, na.rm = T),
            n_unrel = mean(target_answeredN_unrelated, na.rm = T),
            n_rel = mean(target_answeredN_related, na.rm = T),
            .groups = "keep") %>% 
  pivot_wider(data = .,
              names_from = "z_type",
              values_from = c(m_prime:n_rel)) %>% 
  select(-n_unrel_2.5, -n_unrel_3.0, -n_rel_2.5, -n_rel_3.0) %>% 
  mutate(language = "Overall")

prime.lang <- prime.df.all %>% 
  group_by(language, z_type) %>% 
  summarize(m_prime = mean(avgZ_prime, na.rm = T),
            m_unrel = mean(avgZ_RT_unrelated, na.rm = T),
            m_rel = mean(avgZ_RT_related, na.rm = T),
            n_unrel = mean(target_answeredN_unrelated, na.rm = T),
            n_rel = mean(target_answeredN_related, na.rm = T),
            .groups = "keep") %>% 
  pivot_wider(data = .,
              id_cols = "language",
              names_from = "z_type", 
              values_from = c(m_prime:n_rel)) %>% 
  select(-n_unrel_2.5, -n_unrel_3.0, -n_rel_2.5, -n_rel_3.0) %>% 
  bind_rows(prime.overall) %>% 
  select(language, m_prime_All, m_prime_2.5, m_prime_3.0, 
         m_unrel_All, m_unrel_2.5, m_unrel_3.0, 
         m_rel_All, m_rel_2.5, m_rel_3.0, 
         n_unrel_All, n_rel_All
         )
```

```{r priming-table-keep}
flextable(prime.lang) %>% 
  set_header_labels(x = ., 
                    values = c("Language", 
                               "M Z", "M Z2.5", "M Z3.0",
                               "M UR Z", "M UR Z2.5", "M UR Z3.0", 
                               "M R Z", "M R Z2.5", "M R Z3.0", 
                               "N UR", "N R")) %>% 
  colformat_double(
  x = .,
  big.mark = ",", digits = 2, na_str = "N/A",
) %>% 
  add_footer_lines("Note. UR = Unrelated trials, R = related trials, M = mean Z-scored response latency, N = mean number of trials.")
```

## Rescored Acccuracy Priming Scores 

```{r keep-get-priming-keepanswered}
# open all participant data
prime.list <- list.files(
  path = "../05_Data/data_processing/output_data",
  full.names = TRUE,
  recursive = TRUE,
  pattern = "*prime_summary.csv"
)

# only languages we need
langs_trial <- paste(paste0("/", langs, "_answered_prime"), collapse = "|")
prime.list <- prime.list[grepl(langs_trial, prime.list)]

# import files
prime.files <- lapply(prime.list, import)

# give them names 
names(prime.files) <- gsub("../05_Data/data_processing/output_data/priming_data/|_answered_prime_summary.csv|_combo", "", prime.list)

# merge them together
prime.df <- bind_rows(prime.files)
prime.df$language <- rep(names(prime.files), times = unlist(lapply(prime.files, nrow)))
prime.df$z_type <- "All"
```

```{r keep-get-priming2-keepanswered}
# open all participant data
prime.list <- list.files(
  path = "../05_Data/data_processing/output_data",
  full.names = TRUE,
  recursive = TRUE,
  pattern = "*prime_summary_no2.5.csv"
)

# only languages we need
langs_trial <- paste(paste0("/", langs, "_answered_prime"), collapse = "|")
prime.list <- prime.list[grepl(langs_trial, prime.list)]

# import files
prime.files <- lapply(prime.list, import)

# give them names 
names(prime.files) <- gsub("../05_Data/data_processing/output_data/priming_data/|_answered_prime_summary_no2.5.csv|_combo", "", prime.list)

# merge them together
prime.df2 <- bind_rows(prime.files)
prime.df2$language <- rep(names(prime.files), times = unlist(lapply(prime.files, nrow)))
prime.df2$z_type <- "2.5"
```

```{r keep-get-priming3-keepanswered}
# open all participant data
prime.list <- list.files(
  path = "../05_Data/data_processing/output_data",
  full.names = TRUE,
  recursive = TRUE,
  pattern = "*prime_summary_no3.0.csv"
)

# only languages we need
langs_trial <- paste(paste0("/", langs, "_answered_prime"), collapse = "|")
prime.list <- prime.list[grepl(langs_trial, prime.list)]

# import files
prime.files <- lapply(prime.list, import)

# give them names 
names(prime.files) <- gsub("../05_Data/data_processing/output_data/priming_data/|_answered_prime_summary_no3.0.csv|_combo", "", prime.list)

# merge them together
prime.df3 <- bind_rows(prime.files)
prime.df3$language <- rep(names(prime.files), times = unlist(lapply(prime.files, nrow)))
prime.df3$z_type <- "3.0"
```

```{r keep-calc-priming-keepanswered}
# z priming, z unrelated, z related, sample unrelated, sample related
prime.df.all <- bind_rows(
  prime.df,
  prime.df2,
  prime.df3
)

prime.overall <- prime.df.all %>% 
  group_by(z_type) %>% 
  summarize(m_prime = mean(avgZ_prime, na.rm = T),
            m_unrel = mean(avgZ_RT_unrelated, na.rm = T),
            m_rel = mean(avgZ_RT_related, na.rm = T),
            n_unrel = mean(target_answeredN_unrelated, na.rm = T),
            n_rel = mean(target_answeredN_related, na.rm = T),
            .groups = "keep") %>% 
  pivot_wider(data = .,
              names_from = "z_type",
              values_from = c(m_prime:n_rel)) %>% 
  select(-n_unrel_2.5, -n_unrel_3.0, -n_rel_2.5, -n_rel_3.0) %>% 
  mutate(language = "Overall")

prime.lang <- prime.df.all %>% 
  group_by(language, z_type) %>% 
  summarize(m_prime = mean(avgZ_prime, na.rm = T),
            m_unrel = mean(avgZ_RT_unrelated, na.rm = T),
            m_rel = mean(avgZ_RT_related, na.rm = T),
            n_unrel = mean(target_answeredN_unrelated, na.rm = T),
            n_rel = mean(target_answeredN_related, na.rm = T),
            .groups = "keep") %>% 
  pivot_wider(data = .,
              id_cols = "language",
              names_from = "z_type", 
              values_from = c(m_prime:n_rel)) %>% 
  select(-n_unrel_2.5, -n_unrel_3.0, -n_rel_2.5, -n_rel_3.0) %>% 
  bind_rows(prime.overall) %>% 
  select(language, m_prime_All, m_prime_2.5, m_prime_3.0, 
         m_unrel_All, m_unrel_2.5, m_unrel_3.0, 
         m_rel_All, m_rel_2.5, m_rel_3.0, 
         n_unrel_All, n_rel_All
         )
```

```{r priming-table-keepanswered}
flextable(prime.lang) %>% 
  set_header_labels(x = ., 
                    values = c("Language", 
                               "M Z", "M Z2.5", "M Z3.0",
                               "M UR Z", "M UR Z2.5", "M UR Z3.0", 
                               "M R Z", "M R Z2.5", "M R Z3.0", 
                               "N UR", "N R")) %>% 
  colformat_double(
  x = .,
  big.mark = ",", digits = 2, na_str = "N/A",
) %>% 
  add_footer_lines("Note. UR = Unrelated trials, R = related trials, M = mean Z-scored response latency, N = mean number of trials.")
```

## Reliability 

```{r get-reliability-data, eval = F}
# open all priming trial data
prime.list <- list.files(
  path = "../05_Data/data_processing/output_data",
  full.names = TRUE,
  recursive = TRUE,
  pattern = "*prime_trials"
)

# only languages we need
langs_trial <- paste(paste0("/", langs, "_prime"), collapse = "|")
prime.list <- prime.list[grepl(langs_trial, prime.list)]

# import files
prime.files <- lapply(prime.list, import)

# give them names 
names(prime.files) <- gsub("../05_Data/data_processing/output_data/priming_data/|_prime_trials.csv|_combo", "", prime.list)

# merge them together
prime.trials <- bind_rows(prime.files)
prime.trials$language <- rep(names(prime.files), times = unlist(lapply(prime.files, nrow)))

# only people with at least 10 priming trials
prime.people <- prime.trials %>% 
  group_by(observation) %>% 
  summarize(n = n()) %>% 
  filter(n >= 10) %>% 
  pull(observation)

prime.items <- prime.trials %>% 
  group_by(word_combo) %>% 
  summarize(n = n()) %>% 
  filter(n >= 10) %>% 
  pull(word_combo)

prime.trials.keep <- prime.trials %>% 
  filter(keep_participant == "keep") %>% 
  filter(keep_target == "keep") %>% 
  filter(observation %in% prime.people)

prime.items.keep <- prime.trials %>% 
  filter(keep_participant == "keep") %>% 
  filter(keep_target == "keep") %>% 
  filter(word_combo %in% prime.items)

prime.trials.keepanswered <- prime.trials %>% 
  filter(keep_participant_answered == "keep") %>% 
  filter(keep_target == "keep") %>% 
  filter(observation %in% prime.people)

prime.items.keepanswered <- prime.trials %>% 
  filter(keep_participant_answered == "keep") %>% 
  filter(keep_target == "keep") %>% 
  filter(word_combo %in% prime.items)

sb <- function(cor) { (2 * cor) / (1 + cor) }
```

```{r rel-item, eval = F}
save.cor.item <- rep(NA, 100)
save.cor.item.lang <- list()
save.cor.item.keepanswered <- rep(NA, 100)
save.cor.item.keepanswered.lang <- list()

for (i in 1:100){
  
  # keep trials by item 
  prime.items.keep$split <- sample(1:2, nrow(prime.items.keep), 
                                  replace = T) 
  
  # summarize the data 
  person_summary <- prime.items.keep %>% 
    group_by(target_word, type, split, language) %>% #calculate by item, relation, split
    summarize(meanZ_RT = mean(target_Z_RT),
              .groups = "keep") %>% 
    pivot_wider(id_cols = c(target_word, language), 
                names_from = c(type, split),
                values_from = meanZ_RT) %>%  
    mutate(prime_1 = unrelated_1 - related_1, 
           prime_2 = unrelated_2 - related_2)
  
  # overall correlation
  save.cor.item[i] <- sb(cor(person_summary$prime_1, person_summary$prime_2, use = "pairwise.complete.obs"))
  
  # language correlations
  save.cor.item.lang[[i]] <- person_summary %>% 
    group_by(language) %>% 
    summarize(correl = sb(cor(prime_1, prime_2, use = "pairwise.complete.obs")))
  
  
  # keep answered trials by item 
  prime.items.keepanswered$split <- sample(1:2, nrow(prime.items.keepanswered), 
                                  replace = T) 
  
  # summarize the data 
  person_summary <- prime.items.keepanswered %>% 
    group_by(target_word, type, split, language) %>% #calculate by item, relation, split
    summarize(meanZ_RT = mean(target_Z_RT),
              .groups = "keep") %>% 
    pivot_wider(id_cols = c(target_word, language), 
                names_from = c(type, split),
                values_from = meanZ_RT) %>%  
    mutate(prime_1 = unrelated_1 - related_1, 
           prime_2 = unrelated_2 - related_2)
  
  # overall correlation
  save.cor.item.keepanswered[i] <- sb(cor(person_summary$prime_1, person_summary$prime_2, use = "pairwise.complete.obs"))
  
  # language correlations
  save.cor.item.keepanswered.lang[[i]] <- person_summary %>% 
    group_by(language) %>% 
    summarize(correl = sb(cor(prime_1, prime_2, use = "pairwise.complete.obs")))
  
}

rel_item <- list(
  "save.cor.item" = save.cor.item, 
  "save.cor.item.lang" = save.cor.item.lang,
  "save.cor.item.keepanswered" = save.cor.item.keepanswered,
  "save.cor.item.keepanswered.lang" = save.cor.item.keepanswered.lang
  )

save(rel_item, file = "supplemental/reliability_item.RData")
```

```{r rel-person, eval = F}
save.cor.trial <- rep(NA, 100)
save.cor.trial.lang <- list()
save.cor.trial.keepanswered <- rep(NA, 100)
save.cor.trial.keepanswered.lang <- list()

for (i in 1:100){
  
  # keep trials by trial 
  prime.trials.keep$split <- sample(1:2, nrow(prime.trials.keep), 
                                  replace = T) 
  
  # summarize the data 
  person_summary <- prime.trials.keep %>% 
    group_by(observation, type, split, language) %>% #calculate by trial, relation, split
    summarize(meanZ_RT = mean(target_Z_RT),
              .groups = "keep") %>% 
    pivot_wider(id_cols = c(observation, language), 
                names_from = c(type, split),
                values_from = meanZ_RT) %>%  
    mutate(prime_1 = unrelated_1 - related_1, 
           prime_2 = unrelated_2 - related_2)
  
  # overall correlation
  save.cor.trial[i] <- sb(cor(person_summary$prime_1, person_summary$prime_2, use = "pairwise.complete.obs"))
  
  # language correlations
  save.cor.trial.lang[[i]] <- person_summary %>% 
    group_by(language) %>% 
    summarize(correl = sb(cor(prime_1, prime_2, use = "pairwise.complete.obs")))
  
  
  # keep answered trials by trial 
  prime.trials.keepanswered$split <- sample(1:2, nrow(prime.trials.keepanswered), 
                                  replace = T) 
  
  # summarize the data 
  person_summary <- prime.trials.keepanswered %>% 
    group_by(observation, type, split, language) %>% #calculate by trial, relation, split
    summarize(meanZ_RT = mean(target_Z_RT),
              .groups = "keep") %>% 
    pivot_wider(id_cols = c(observation, language), 
                names_from = c(type, split),
                values_from = meanZ_RT) %>%  
    mutate(prime_1 = unrelated_1 - related_1, 
           prime_2 = unrelated_2 - related_2)
  
  # overall correlation
  save.cor.trial.keepanswered[i] <- sb(cor(person_summary$prime_1, person_summary$prime_2, use = "pairwise.complete.obs"))
  
  # language correlations
  save.cor.trial.keepanswered.lang[[i]] <- person_summary %>% 
    group_by(language) %>% 
    summarize(correl = sb(cor(prime_1, prime_2, use = "pairwise.complete.obs")))
  
}

rel_trial <- list(
  "save.cor.trial" = save.cor.trial, 
  "save.cor.trial.lang" = save.cor.trial.lang,
  "save.cor.trial.keepanswered" = save.cor.trial.keepanswered,
  "save.cor.trial.keepanswered.lang" = save.cor.trial.keepanswered.lang
  )

save(rel_trial, file = "supplemental/reliability_trial.RData")
```

```{r rel-item-results}
# see code above 
load(file = "supplemental/reliability_item.RData")
load(file = "supplemental/reliability_trial.RData")
# rel_item
# rel_trial
```

Item reliability was calculated by randomly splitting priming trials into two halves, calculating *Z*-score priming for each half, and correlating those scores by item. Person level reliability was calculated in a similar fashion by splitting participant related-unrelated trials in half and calculating priming as the average unrelated *Z*-scored response latency minus the related *Z*-scored response latency, and correlating the two priming scores. The Spearman-Brown prophecy formula was applied to these correlations to calculate total reliability. This procedure was repeated 100 times, and average scores were calculated. Table X shows the reliability scores for person and items. The average reliability for items was `r apa_num(mean(rel_item$save.cor.item), gt1 = FALSE)` and for people was `r apa_num(mean(rel_trial$save.cor.trial), gt1 = FALSE)`. 

```{r reliability-table-keep}
rel.lang <- bind_rows(rel_item$save.cor.item.lang) %>% 
  group_by(language) %>% 
  summarize(correl = mean(correl), .groups = "keep") %>% 
  full_join(
     bind_rows(rel_trial$save.cor.trial.lang) %>% 
  group_by(language) %>% 
  summarize(correl = mean(correl), .groups = "keep"), 
  by = "language"
  )

flextable(rel.lang) %>% 
  set_header_labels(x = ., 
                    values = c("Language", "Item Reliability", "Person Reliability")) %>% 
  colformat_double(
  x = .,
  big.mark = ",", digits = 2, na_str = "N/A",
) 

```

For rescored accuracy participants the average reliability for items was `r apa_num(mean(rel_item$save.cor.item.keepanswered), gt1 = FALSE)` and for people was `r apa_num(mean(rel_trial$save.cor.trial.keepanswered), gt1 = FALSE)`. Table X shows the same information split by language for rescored accuracy participants. 

```{r reliability-table-keepanswered}
rel.lang <- bind_rows(rel_item$save.cor.item.keepanswered.lang) %>% 
  group_by(language) %>% 
  summarize(correl = mean(correl), .groups = "keep") %>% 
  full_join(
     bind_rows(rel_trial$save.cor.trial.keepanswered.lang) %>% 
  group_by(language) %>% 
  summarize(correl = mean(correl), .groups = "keep"), 
  by = "language"
  )

flextable(rel.lang) %>% 
  set_header_labels(x = ., 
                    values = c("Language", "Item Reliability", "Person Reliability")) %>% 
  colformat_double(
  x = .,
  big.mark = ",", digits = 2, na_str = "N/A",
) 
```


