---
title: "Confirmatory Hypothesis Testing - ZPID Data"
author: "Erin M. Buchanan"
date: "Last Update `r Sys.Date()`"
output:
  html_document:
    df_print: paged
    toc: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, size="scriptsize")
def.chunk.hook <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})
```

This demonstration is for the three languages provided in the ZPID funded data. Please see the full manuscript for all langauges. https://osf.io/q4fjy/

## Libraries

```{r}
library(dplyr)
library(psych)
library(tidyr)
library(ggplot2)
library(rio)
library(faux)
set.seed(58902)
library(nlme)
library(MuMIn)
library(performance)
library(parameters)

```

## Import the Files

We will import these files from our data folder for the final analyses. This example analysis examines the Semantic Priming Project data to simulate how to answer questions. The descriptive statistics file has examples of the processing and cleaning data  

```{r}
targets_only <- 
  bind_rows(
    import("../05_Data_real/output_data/ru_prime_data.csv") %>% 
      mutate(Language = "Russian"), 
     import("../05_Data_real/output_data/tr_prime_data.csv") %>% 
      mutate(Language = "Turkish"),
     import("../05_Data_real/output_data/ko_prime_data.csv") %>% 
      mutate(Language = "Korean")
  )
```

## Hypothesis 1 

Is semantic priming a non-zero effect? 

### Model Results

```{r}
# run the analysis
hyp1 <- lm(avgZ_prime ~ 1, data = targets_only)

# print the results
summary(hyp1)
parameters(hyp1)
model_performance(hyp1)
```

## Hypothesis 2

Is semantic priming consistent by language? 

### Model Reesults

```{r}
# run the model
hyp2 <- lme(avgZ_prime ~ 1, 
            data = targets_only, 
            method = "REML", 
            random = ~1|Language)

# print the results
summary(hyp2)
parameters(hyp2)
model_performance(hyp2)
intervals(hyp2)

# compare models
AIC(hyp1)
AIC(hyp2)

# effect size
r.squaredGLMM(hyp2)
```

### Graph Results

```{r}
# example plot
ggplot(targets_only, aes(Language, avgZ_prime)) +
  stat_summary(fun.data = mean_cl_normal, 
               geom = "errorbar", 
               width = .2, 
               position = position_dodge(width = .2)) + 
  stat_summary(fun = mean,
               geom = "point", 
               position = position_dodge()) + 
  xlab("Language") + 
  ylab("Z Score Priming") +
  theme_classic() + 
  coord_flip() + 
  geom_hline(yintercept = 0)
```
