---
title: "Confirmatory Hypothesis Testing"
author: "Erin M. Buchanan"
date: "Last Update `r Sys.Date()`"
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, size="scriptsize")
def.chunk.hook <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})
```

## Libraries

```{r}
library(dplyr)
library(psych)
library(tidyr)
library(ggplot2)
library(rio)
library(faux)
set.seed(58902)
library(nlme)
library(MuMIn)
```

## Import the Files

We will import these files from our data folder for the final analyses. This example analysis examines the Semantic Priming Project data to simulate how to answer questions. The descriptive statistics file has examples of the processing and cleaning data  

```{r}
# targets_only <- read.csv("../05_Data/output_data/prime_data.csv")
# targets_only_no2.5 <- read.csv("../05_Data/output_data/prime_data_no2.5.csv")
# targets_only_no3.0 <- read.csv("../05_Data/output_data/prime_data_no3.0.csv")

SPP <- import("spp_ldt_prime.xlsx")
```

## Languages

This demonstration with the SPP only has English data. However, we will have 10 languages for our completed data. Therefore, we will simulate data that is nearly similar for 10 other languages (no heterogeneity) and different for the other 10 languages (heterogeneity).

```{r}
# use our names so we can update this code easier
sim_data <- SPP %>% 
  select(long_1st_rel, long_1st_un, firstassoc_fas, target) %>% 
  dplyr::rename(avgZ_RT_related = long_1st_rel) %>% 
  dplyr::rename(avgZ_RT_unrelated = long_1st_un) %>% 
  mutate(Language = "English") %>% 
  sample_n(1000) %>% 
  mutate(samplesize_related = round(rnorm(1000, mean = 75, sd = 10)), 
         samplesize_unrelated = round(rnorm(1000, mean = 75, sd = 10)), 
         seZ_RT_related = round(rnorm(1000, mean = .09, sd = .02), digits = 3),
         seZ_RT_unrelated = round(rnorm(1000, mean = .09, sd = .02), digits = 3)) 

# build fake data
lang2 <- sim_df(data = sim_data, n = nrow(sim_data), id = "target")
lang3 <- sim_df(data = sim_data, n = nrow(sim_data), id = "target")
lang4 <- sim_df(data = sim_data, n = nrow(sim_data), id = "target")
lang5 <- sim_df(data = sim_data, n = nrow(sim_data), id = "target")
lang6 <- sim_df(data = sim_data, n = nrow(sim_data), id = "target")
lang7 <- sim_df(data = sim_data, n = nrow(sim_data), id = "target")
lang8 <- sim_df(data = sim_data, n = nrow(sim_data), id = "target")
lang9 <- sim_df(data = sim_data, n = nrow(sim_data), id = "target")
lang10 <- sim_df(data = sim_data, n = nrow(sim_data), id = "target")

lang2$target <- lang3$target <- lang4$target <- lang5$target <- lang6$target <- lang7$target <- lang8$target <- lang9$target <- lang10$target <- sim_data$target

lang2$Language <- "Language 2"
lang3$Language <- "Language 3"
lang4$Language <- "Language 4"
lang5$Language <- "Language 5"
lang6$Language <- "Language 6"
lang7$Language <- "Language 7"
lang8$Language <- "Language 8"
lang9$Language <- "Language 9"
lang10$Language <- "Language 10"

sim_data_same <- rbind(sim_data, lang2, lang3, lang4, lang5, lang6, lang7, lang8, lang9, lang10) %>% 
  mutate(samplesize_related = round(samplesize_related), 
         samplesize_unrelated = round(samplesize_unrelated),
         avgZ_prime = avgZ_RT_unrelated - avgZ_RT_related)

tapply(sim_data_same$avgZ_prime, sim_data_same$Language, mean)

sim_data_diff <- sim_data_same %>% 
  group_by(Language) %>% 
  mutate(avgZ_prime = avgZ_prime + rnorm(1, mean = 0, sd = .20))

tapply(sim_data_diff$avgZ_prime, sim_data_diff$Language, mean)
```

## Hypothesis 1 - Languages Same

Is semantic priming a non-zero effect? 

```{r}
hyp1 <- lm(avgZ_prime ~ 1, data = sim_data_same)
summary(hyp1)
confint(hyp1)
```

## Hypothesis 2 - Languages Same

Is semantic priming consistent by language? 

```{r}
hyp2 <- lme(avgZ_prime ~ 1, 
            data = sim_data_same, 
            method = "REML", 
            random = ~1|Language)
summary(hyp2)

intervals(hyp2)

AIC(hyp1)
AIC(hyp2)

r.squaredGLMM(hyp2)
```

```{r}
# example plot
ggplot(sim_data_same, aes(Language, avgZ_prime)) +
  stat_summary(fun.data = mean_cl_normal, 
               geom = "errorbar", 
               width = .2, 
               position = position_dodge(width = .2)) + 
  stat_summary(fun = mean,
               geom = "point", 
               position = position_dodge()) + 
  xlab("Language") + 
  ylab("Z Score Priming") +
  theme_classic() + 
  coord_flip() + 
  geom_hline(yintercept = 0)

```


## Hypothesis 1 - Languages Different

Is semantic priming a non-zero effect? 

```{r}
hyp1 <- lm(avgZ_prime ~ 1, data = sim_data_diff)
summary(hyp1)
confint(hyp1)
```

## Hypothesis 2 - Languages Different 

Is semantic priming consistent by language? 

```{r}
hyp2 <- lme(avgZ_prime ~ 1, 
            data = sim_data_diff, 
            method = "REML", 
            random = ~1|Language)
summary(hyp2)

intervals(hyp2)

AIC(hyp1)
AIC(hyp2)

r.squaredGLMM(hyp2)
```

```{r}
# example plot
ggplot(sim_data_diff, aes(Language, avgZ_prime)) +
  stat_summary(fun.data = mean_cl_normal, 
               geom = "errorbar", 
               width = .2, 
               position = position_dodge(width = .2)) + 
  stat_summary(fun = mean,
               geom = "point", 
               position = position_dodge()) + 
  xlab("Language") + 
  ylab("Z Score Priming") +
  theme_classic() + 
  coord_flip() + 
  geom_hline(yintercept = 0)

```

