---
title: "Author_List"
author: "erin buchanan"
date: "Last Knitted: `r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
#libraries
library(gsheet)
library(rio)
library(flextable)
library(dplyr)
```

```{r}
#grab tenzing information
lab_gsheet <- gsheet2tbl("https://docs.google.com/spreadsheets/d/15f0OaG_R6WK_hOIhBwwQ3YEzrjbsVkUT8FqTQilR4zA/edit?usp=sharing")

admin_team <- c(lab_gsheet$PSA_ID[lab_gsheet$Tier == 1 | #erin/kelly
                                    lab_gsheet$Tier == 1.1 | #admin
                                    lab_gsheet$Tier == 3]) #sav
```

```{r}
#grab download canvas
canvas_contributions <- import("contributions.csv")

#drop the first line
canvas_contributions <- canvas_contributions[-1 , ]

#rename the columns so windows isn't dumb
colnames(canvas_contributions) <- c("Student", "Canvas_ID", "PSA_ID", "Login_Email", 
                                    "Integration_ID", "Section", "words2many_formating",
                                    "subs2strudel_spelling", "power_dataset",
                                    "power_coding", "power_writing", "collab_agree", 
                                    "submit_irb", "SPAML_RR", "team_list", "fall2021_pres",
                                    "SPAML_comments", "fake_check", "spring_data",
                                    "cc_points", "cf_points", "cc_score", 
                                    "cuc_score", "cf_score", "cuf_score", 
                                    "current_points", "final_points",
                                    "current_score", "uc_score", "final_score", "uf_score")
                                    
# drop crap we don't need
good_cols <- c("Student", "PSA_ID", "Login_Email", "words2many_formating", 
               "subs2strudel_spelling", "power_dataset", "power_coding", 
               "power_writing", "collab_agree",  "submit_irb", "SPAML_RR")
canvas_contributions <- canvas_contributions[ , good_cols] 
```

## Fill in Missing PSA_IDs

```{r}
# check for blank PSA_IDs
cat("Contribution Google Doc  \n")
lab_gsheet$`Full Name`[is.na(lab_gsheet$PSA_ID)]

# check for blank in Canvas
cat("Canvas Blank IDs  \n")
canvas_contributions$Student[is.na(canvas_contributions$PSA_ID)]
```

## Check for Duplicated IDs 

```{r}
# for the registered report they have to do the RR survey and contributor survey
combined_sheet <- merge(lab_gsheet, 
                        canvas_contributions[ , c("PSA_ID", "SPAML_RR", "collab_agree")], 
                        by.x = "PSA_ID", by.y = "PSA_ID", all = T) 

# make sure not duplicated PSAID
if (sum(duplicated(combined_sheet$PSA_ID)) > 0){
  combined_sheet$`Full Name`[duplicated(combined_sheet$PSA_ID)]
}
```

## Completed RR Not on Our Sheet

```{r}
autofit(flextable(subset(combined_sheet, 
                 SPAML_RR > 0 && is.na(Tier), 
                 select = c(PSA_ID, `Full Name`, `Email address`))))
```

## Did Not Complete RR

```{r}
autofit(flextable(
  combined_sheet %>% 
    filter(is.na(SPAML_RR) | SPAML_RR == 0) %>% 
    filter(!is.na(Tier)) %>% 
    filter(!(PSA_ID %in% admin_team)) %>% 
    select(PSA_ID, `Full Name`, `Email address`)
))
```

## Did Not Complete Collaborator Agreement 

```{r}
autofit(flextable(
  combined_sheet %>% 
    filter(is.na(collab_agree) | collab_agree == 0) %>% 
    filter(!is.na(Tier)) %>% 
    filter(!(PSA_ID %in% admin_team)) %>% 
    select(PSA_ID, `Full Name`, `Email address`)
))
```

## Authorship

```{r}
# print out authorship 

# take out double spaces made by concat in gsheet
combined_sheet$`Full Name` <- gsub("  ", " ", combined_sheet$`Full Name`)
combined_sheet$`Full Affiliation` <- gsub("; ;", "", combined_sheet$`Full Affiliation`)
combined_sheet$`Full Affiliation` <- gsub(";$", "", combined_sheet$`Full Affiliation`)

ordered_author <- combined_sheet

# fill in collab + RR admin team
ordered_author[ordered_author$PSA_ID %in% admin_team , c("SPAML_RR", "collab_agree")] <- 1
  
# drop people who didn't fill out stuff
ordered_author <- subset(ordered_author, 
                         SPAML_RR > 0 &
                           collab_agree > 0)

# randomize 2 rest are in order 
set.seed(5843902)
  # get rows with 2
  rows_2 <- ordered_author$PSA_ID[grep("^2", ordered_author$Tier)]
  # randomize
  rows_2 <- sample(rows_2, length(rows_2), replace = FALSE)
  # author PSA ID order
  PSA_ID_sorted <- c(lab_gsheet$PSA_ID[lab_gsheet$Tier == 1], #tier 1
      lab_gsheet$PSA_ID[lab_gsheet$Tier == 1.1], #tier 1.1
      lab_gsheet$PSA_ID[lab_gsheet$Tier == 1.2], #tier 1.2
      rows_2, #tier 2
      lab_gsheet$PSA_ID[lab_gsheet$Tier == 3])
  # put back together
  ordered_author <- ordered_author[match(PSA_ID_sorted, ordered_author$PSA_ID), ]
  
  
ordered_author$full <- paste(ordered_author$`Full Name`, 
                             ordered_author$`Full Affiliation`, 
                             #ordered_author$`Email address`, 
                             sep = ", ")


```

`r paste(ordered_author$full, collapse = "  \n")`

### For second round RR sub, these are new

`r paste(ordered_author$full[ordered_author$Tier == "2.1"], collapse = "  \n")`

## Credit

```{r}
ordered_author$Conceptualization <- ifelse(ordered_author$Conceptualization == TRUE, "Conceptualization", "")

ordered_author$`Data curation` <- ifelse(ordered_author$`Data curation` == TRUE, "Data Curation", "")

ordered_author$`Formal analysis` <- ifelse(ordered_author$`Formal analysis` == TRUE, "Formal Analysis", "")

ordered_author$`Funding acquisition` <- ifelse(ordered_author$`Funding acquisition` == TRUE, "Funding Acquisition", "")

ordered_author$Investigation <- ifelse(ordered_author$Investigation == TRUE, "Investigation", "")

ordered_author$Methodology <- ifelse(ordered_author$Methodology == TRUE, "Methodology", "")

ordered_author$`Project administration` <- ifelse(ordered_author$`Project administration` == TRUE, "Project Administration", "")

ordered_author$Resources <- ifelse(ordered_author$Resources == TRUE, "Resources", "")

ordered_author$Software <- ifelse(ordered_author$Software == TRUE, "Software", "")

ordered_author$Supervision <- ifelse(ordered_author$Supervision == TRUE, "Supervision", "")

ordered_author$Validation <- ifelse(ordered_author$Validation == TRUE, "Validation", "")

ordered_author$Visualization <- ifelse(ordered_author$Visualization == TRUE, "Visualization", "")

ordered_author$`Writing - original draft` <- ifelse(ordered_author$`Writing - original draft` == TRUE, "Writing - Original Draft", "")

ordered_author$`Writing - review & editing` <- ifelse(ordered_author$`Writing - review & editing` == TRUE, "Writing - Review & Editing", "")

ordered_author$credit <- paste(paste(ordered_author$`Full Name`, ": ", sep = ""), 
                               ordered_author$Conceptualization, 
                               ordered_author$`Data curation`, 
                               ordered_author$`Formal analysis`, 
                               ordered_author$`Funding acquisition`, 
                               ordered_author$Investigation, 
                               ordered_author$Methodology,
                               ordered_author$`Project administration`, 
                               ordered_author$Resources, 
                               ordered_author$Software, 
                               ordered_author$Supervision, 
                               ordered_author$Validation, 
                               ordered_author$Visualization, 
                               ordered_author$`Writing - original draft`, 
                               ordered_author$`Writing - review & editing`, 
                               sep = ", ")


ordered_author$credit <- gsub(" ,", "", ordered_author$credit)
```

`r paste(ordered_author$credit, collapse = "  \n")`

### For second round RR sub, these are new

`r paste(ordered_author$credit[ordered_author$Tier == "2.1"], collapse = "  \n")`

```{r echo = F, eval = F, include = F}
ordered_author %>% filter(Tier == "2.1") %>% 
  select(Firstname, `Middle name`, Surname, `Email address`, 
         `Primary affiliation`, `Secondary affiliation`, `Full Affiliation`, PSA_ID) %>% 
  export(., "nhb_utf8_2.xlsx", "xlsx")
```

